---
title: "location-nodscov2"
author: "Olivier GAUFRÈS"
date: "2024-05-07"
output: html_document
---

## Subdivide contact data into 30 seconds time steps and save interaction clusters 
```{r Subdividing interactions}
# Global interaction object
begin_date <- min(interactions$date_posix)
end_date <- max(interactions$date_posix + interactions$length)
time_spent <- difftime(end_date, begin_date, units = "secs")  

n_subdivisions <- as.numeric(time_spent) / 30 ## Time spent * hours * minutes * 2 (number of time subdivisions)
## floor because of the manner we extract the interactions (=30sec, i.e. at  the end, interactions are <30sec -> we dont take these)

# # # t = 1 -> [0,30[sec
# global_interaction <- lapply(1:n_subdivisions, function(t){
#   interactions_t <- interactions %>%
#     filter(date_posix <= (begin_date + (t-1)*30), date_posix + length >= begin_date + (t)*30 ) %>%
#     mutate(time = t) %>%
#     select(from, to, time, from_status, to_status)
# 
#   return(interactions_t)
# })
# save(global_interaction, file = file.path(nodscov2_synthetic_path, "loc", "global_interaction.rda"))
# 
# # List of interaction clusters
# clusters <- lapply(global_interaction, function(df) {
#   # df to non oriented graph based on interaction happening at time t
#   graph <- graph_from_data_frame(df, directed = FALSE)
#   # Extract connected component
#   clusters <- components(graph)$membership
#   # clusters to list (unique list of individual)
#   clusters_list <- lapply(unique(clusters), function(i) {
#     #for each cluster i, we extract the vertices/nodes of the graph -> individual names in each clusters
#     as.character(V(graph)[clusters == i]$name)
#   })
#   return(clusters_list)
# })
# save(clusters, file = file.path(nodscov2_synthetic_path, "loc", "clusters.rda"))

load(file.path(nodscov2_synthetic_path, "loc", "global_interaction.rda"))
load(file.path(nodscov2_synthetic_path, "loc", "clusters.rda"))
```

## Location inference for all individuals during close-proximity interactions
```{r Loc for interactions}
############################################################
## ASSIGNING location FOR THE INDIVIDUALS INTERACTING ##
############################################################
# This code chunk uses the following input data
    # n_subdivisions
    # id_total
    # id_medical
    # id_paramedical
    # begin_date
    # global_interaction
    # clusters

# It returns the following objects
    # global_location : list with the localisation of all interaction clusters
    # cluster info list


# ## Store info when there is more than one patient in clusters -> fix later
# cluster_info_list <- list()
# global_location <- list()
# 
# global_location <- lapply(1:n_subdivisions, function(t) {
#   location_t <- data.frame(id = id_total, location = NA, time = t) ##only for individuals that interact
#   # Interactions at time t
#   interactions_t <- global_interaction[[t]] %>% mutate(location = NA)
#   clusters_t <- clusters[[t]]
#   # For each clusters of individuals at time t
#   lapply(clusters_t, function(cluster) {
# 
#     # Remove duplicates if any
#     cluster = sort(unique(cluster))
# 
#     ###########################
#     ## CLUSTER WITH PATIENTS ##
#     ###########################
#     # IF THERE IS NO PATIENTS
#     NO_PATIENT <- all(!grepl("^PA-", cluster))
#     # IF THERE IS ONLY ONE PATIENT IN THE CLUSTER
#     ONE_PATIENT <- sum(grepl("^PA-", cluster)) == 1
#     one_patient_room <- ifelse(ONE_PATIENT, rooms$id_room[rooms$id %in% cluster[grepl("^PA-", cluster)]], "-2")
#     ## IF IN DOUBLE ROOM (MUST BE ONLY THE TWO PATIENTS, NOT THE TWO PATIENT + ANOTHER PATIENT)
#     patient_rooms = unique(rooms$id_room[rooms$id %in% cluster[grepl("^PA-", cluster)]])
#     IN_DOUBLE_ROOM_N1 <- !NO_PATIENT & all(patient_rooms == double_rooms_id[1])
#     IN_DOUBLE_ROOM_N2 <- !NO_PATIENT & all(patient_rooms == double_rooms_id[2])
#     # IF THERE IS MULTIPLE PATIENTS IN THE CLUSTER (AND NOT IN DOUBLE ROOM)
#     MULTIPLE_PATIENT <- sum(grepl("^PA-", cluster)) > 1 & !(IN_DOUBLE_ROOM_N1 | IN_DOUBLE_ROOM_N2)
# 
#     ##############################
#     ## CLUSTER WITHOUT PATIENTS ##
#     ##############################
#     NO_MEDICAL <- sum(cluster %in% id_medical) == 0
#     NO_PARAMEDICAL <- sum(cluster %in% id_paramedical) == 0
# 
#     ONLY_PARAMEDICAL <- NO_PATIENT & NO_MEDICAL
#     ONLY_MEDICAL <- NO_PATIENT & NO_PARAMEDICAL
#     MEDICAL_AND_PARAMEDICAL <- NO_PATIENT & !NO_MEDICAL & !NO_PARAMEDICAL
# 
#     #####################
#     ## TIME CONDITIONS ##
#     #####################
#     time_t <- begin_date + (t-1)*30
#     DAY <- between(hour(time_t), 7, 20)
#     NIGHT <- between(hour(time_t), 21, 24) | between(hour(time_t), 0, 6)
# 
#     #################################
#     ## location OF THE CLUSTER ##
#     #################################
#     cluster_location <- case_when(
#       MULTIPLE_PATIENT ~ rooms$id_room[rooms$id == "ALL"],
#       IN_DOUBLE_ROOM_N1 ~ as.character(double_rooms_id[1]),
#       IN_DOUBLE_ROOM_N2 ~ as.character(double_rooms_id[2]),
#       ONE_PATIENT ~ one_patient_room,
#       ONLY_MEDICAL ~ rooms$id_room[rooms$id == "M-PE"], ## ONLY MEDICAL INTERACTING -> OFFICE
#       ONLY_PARAMEDICAL ~ rooms$id_room[rooms$id == "PM-PE"], ## ONLY PARAMEDICAL INTERACTING -> NURSING STATION
#       MEDICAL_AND_PARAMEDICAL ~ rooms$id_room[rooms$id == "PM-PE"], ## ONLY MED AND PARAMED -> NURSING STATION
#       .default = "-3"
#     )
#     ## Assign the location for individuals inside the cluster
#     # <<- to edit location_t defined outside clusters_t's lapply scope
#     interactions_t$location[interactions_t$from %in% cluster] <<- cluster_location ## if from is in the cluster, to will be also
#     location_t$location[location_t$id %in% cluster] <<- cluster_location
# 
#     ## MULTIPLE PATIENTS IN THE CLUSTER --> TEMPORARY, FIXED LATER
#     if (MULTIPLE_PATIENT) {
#       cluster_possible_location <- rooms$id_room[rooms$id %in% cluster[grepl("^PA-", cluster)]]
#       cluster_info <- data.frame(time = t, Patients = cluster[grepl("^PA-", cluster)], cluster = toString(cluster))
#       cluster_info_list <<- append(cluster_info_list, list(cluster_info))
#     }
#   })
# 
#   ## ADD THE location IN GLOBAL_INTERACTION (we could have added the cluster id but its useless for now)
#   global_interaction[[t]] <<- interactions_t
#   return(location_t)
# })

#save(global_location, file = file.path(nodscov2_synthetic_path, "loc", "global_location.rda"))
load(file.path(nodscov2_synthetic_path, "loc", "global_location.rda"))
```

## Smooth individual trajectories and associate location when individuals are 
## present without close-proximity interactions  
```{r}
# SMOOTH INDIVIDUAL TRAJECTORIES
threshold = 90*2 # 30*2 60*2

# Get the data in wide format
locations = do.call("rbind", global_location) %>%
  pivot_wider(names_from = id, values_from = location) %>%
  arrange(time) %>%
  select(-time) 
rm(global_location)

# Add when individuals are not present in the ward and add their room 
# otherwise (Patients)
identical(names(locations[, id_patient]), id_patient)
locations[,id_patient[id_patient %in% id_interacting]] = as_tibble(mapply(
  patient_locations, patient_id = id_patient[id_patient %in% id_interacting], patient_loc = locations[, id_patient[id_patient %in% id_interacting]],
  MoreArgs = list(admission = admission, begin_date = begin_date, end_date = end_date, patient_rooms = patient_rooms)
  ))

# Add when individuals are not present in the ward and smooth
# their individual trajectory (HCW)
identical(names(locations[, id_hcw]), id_hcw)
patient_rooms_ids = as.character(sort(unique(patient_rooms$room)))
locations[,id_hcw] = as_tibble(mapply(
  hcw_locations, hcw_id = id_hcw, hcw_loc = locations[,id_hcw], 
  MoreArgs= list(threshold = threshold, agenda = agenda, admission = admission, begin_date = begin_date, end_date = end_date, patient_rooms_ids = patient_rooms_ids, id_medical = id_medical)
  ))

# Convert locations into a list
write.csv2(locations, file.path(nodscov2_synthetic_path, "loc", paste0("locations_long_format_", threshold, ".csv")), quote = F, row.names = F)
locations = locations %>%
    mutate(time = 1:n()) %>%
    pivot_longer(-time, names_to = "id", values_to = "location")
global_location = split(locations, f = locations$time)
rm(locations)
```

## Save to an .RData file
```{r Save to .RData}

```


## SHIFTS INFERENCE
```{r Shifts}
# # Pivot -> get all int for each individual
# df_long <- data %>%
#   mutate(date_posix_end = date_posix_first + length) %>%
#   pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
#   arrange(individual, date_posix_first)
# 
# # Time between 2 interactions for each individual (lag get the previous )
# df_long <- df_long %>%
#   group_by(individual) %>%
#   mutate(test_filter = date_posix_first - lag(date_posix_end)) %>%
#   filter(test_filter > 0 | is.na(test_filter)) %>%
#   mutate(time_diff = difftime(date_posix_first, lag(date_posix_end), units = "mins"))
# 
# 
# time_threshold <- 60*1.5
# 
# df_long <- df_long %>%
#   mutate(new_shift = ifelse(is.na(time_diff) | time_diff > time_threshold, 1, 0)) %>%
#   group_by(individual) %>%
#   mutate(shift_id = cumsum(new_shift))
# 
# shifts <- df_long %>%
#   group_by(individual, shift_id) %>%
#   summarise(
#     start_time = min(date_posix_first),
#     end_time = max(date_posix_end),
#     shift_length = as.numeric(difftime(max(date_posix_end), min(date_posix_first), units = "hours")),
#     .groups = 'drop'
#   ) %>%
#   arrange(individual, shift_id) %>%
#   left_join(admission %>% select(id,cat,status), by = c("individual" = "id")) %>%
#   filter(status == "PE")

```

## SMOOTHING (SUCCESSIVE INTERACTION IN THE SAME ROOM WITH <5min GAP)
```{r}
# # Function to smooth individual trajectories
# smoothing_location <- function(global_interaction, global_location) {
#   interactions <- do.call("rbind", global_interaction)
#   locations <- do.call("rbind", global_location)
#   smoothed_loc <- data.frame()
#   
#   interactions_long <- interactions %>%
#     pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
#     arrange(individual, time)
# 
#   for (ind in unique(interactions_long$individual)) {
#     ind_interactions <- interactions_long %>% filter(individual == ind) %>% arrange(time)
#     ind_locations <- locations %>% filter(id == ind)
#     
#     if (nrow(ind_interactions) > 2) {
#       for (i in 2:nrow(ind_interactions)) {
#         time_gap <- ind_interactions$time[i] - ind_interactions$time[i - 1]
#         
#         if (time_gap == 2){
#           previous_loc <- ind_locations %>% filter(time == ind_interactions$time[i - 1]) %>% pull(location)
#           current_loc <- ind_locations %>% filter(time == ind_interactions$time[i]) %>% pull(location)
#           if (previous_loc == current_loc & current_loc %in% id_room_patient){
#             ind_locations$location[ind_locations$time == ind_interactions$time[i] - 1] <- current_loc
#             }
#         }
#         if (time_gap > 2 & time_gap <= 10) {
#           previous_loc <- ind_locations %>% filter(time == ind_interactions$time[i - 1]) %>% pull(location)
#           current_loc <- ind_locations %>% filter(time == ind_interactions$time[i]) %>% pull(location)
#           if (previous_loc == current_loc & current_loc %in% id_room_patient){
#             for (t in (ind_interactions$time[i - 1] + 1):(ind_interactions$time[i] - 1)) {
#             ind_locations$location[ind_locations$time == t] <- current_loc
#             }
#           }
#         }
#       }
#     }
#     smoothed_loc <- rbind(smoothed_loc, ind_locations)
#   }
#   smoothed_loc <- smoothed_loc %>% arrange(id, time)
#   return(smoothed_loc)
# }
# 
# 
# smoothed_global_interaction <- smoothing_location(global_interaction, global_location)
# 
# ## Transform to list object
# global_location <- lapply(1:n_subdivisions, function(t) {
#   location_t <- smoothed_global_interaction %>% filter(time == t) %>% arrange(id)
#   return(location_t)
# })
# 
# rm(smoothed_global_interaction)
```

## SMOOTHING (ADDING CORRIDOR BEFORE AN INTERACTION)
```{r}
# smoothing_corridor <- function(global_interaction, global_location) {
#   interactions <- do.call(rbind, global_interaction)
#   locations <- do.call(rbind, global_location)
#   smoothed_corridor <- data.frame()
#   
#   interactions_long <- interactions %>%
#     pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
#     arrange(individual, time)
#   id_corridor <- rooms[rooms$room == "Corridor", "id_room"]
# 
#   for (ind in unique(interactions_long$individual)) {
#     ind_interactions <- interactions_long %>% filter(individual == ind) %>% arrange(time)
#     ind_locations <- locations %>% filter(id == ind)
#     
#     if (nrow(ind_interactions) > 2) {
#       for (i in 2:nrow(ind_interactions)) {
#         time_gap <- ind_interactions$time[i] - ind_interactions$time[i - 1]
#         
#         if (time_gap == 2){
#           ind_locations[ind_locations$time == ind_interactions$time[i] - 1, "location"] <- id_corridor
#         }
#         if (time_gap > 2) {
#           ind_locations[ind_locations$time == ind_interactions$time[i - 1] + 1, "location"] <- id_corridor
#           ind_locations[ind_locations$time == ind_interactions$time[i] - 1, "location"] <- id_corridor
#         }
#       }
#     }
#     smoothed_corridor <- rbind(smoothed_corridor, ind_locations)
#   }
#   smoothed_corridor <- smoothed_corridor %>% arrange(id, time)
#   return(smoothed_corridor)
# }
# 
# smoothed_corridor_global_interaction <- smoothing_corridor(global_interaction, global_location)
# 
# ## DF TO LIST
# global_location <- lapply(1:n_subdivisions, function(t) {
#   location_t <- smoothed_corridor_global_interaction %>% filter(time == t) %>% arrange(id)
#   return(location_t)
# })
# 
# rm(smoothed_corridor_global_interaction)
```

## FILL location FOR PATIENTS
```{r}
# global_location <- lapply(1:n_subdivisions, function(t) {
#   location_t <- global_location[[t]]
#   for (ind in id_patient) {
#     if (is.na(location_t[location_t$id == ind, "location"])) {
#       location_t[location_t$id == ind, "location"] <- rooms[rooms$id == ind, "id_room"]
#     }
#   }
#   
#   return(location_t)
# })
```

## location INFERENCE - NO INTERACTION (PATIENTS STAY IN THEIR ROOM, SO WE ONLY CHECK/FILL HCW)
```{r Loc t1}
# ################################################################
# ## ASSIGNING location FOR THE INDIVIDUALS NOT INTERACTING ##
# ################################################################
# 
# ############
# ## t == 1 ##
# ############
# 
# # FIRST SUBDIVISION 
# ## RULES TO BE DEFINED
# ## IF NOT INTERACTING AT t == 1, assign location to -1 (NOT HERE)
# global_location[[1]]$location <- ifelse(is.na(global_location[[1]]$location), -1, global_location[[1]]$location )
```

```{r Loc t2}
# ############
# ## t == 2 ##
# ############
# 
# ## SECOND SUBDIVISION
# location_t1 <- global_location[[1]]
# location_t2 <- global_location[[2]]
# 
# id_not_interacting_t2 <- location_t2 %>% filter(is.na(location)) %>% pull(id)
# id_room_t1 <- location_t1 %>% filter(location %in% id_room_patient) %>% pull(id)
# id_corridor_t1 <- location_t1 %>% filter(location == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
# id_medical_restroom_t1 <- location_t1 %>% filter(location == rooms[rooms$id == "R-M-PE", "id_room"]) %>% pull(id)
# id_paramedical_restroom_t1 <- location_t1 %>% filter(location == rooms[rooms$id == "R-PM-PE", "id_room"]) %>% pull(id)
# id_nursing_station_t1 <- location_t1 %>% filter(location == rooms[rooms$id == "PM-PE", "id_room"]) %>% pull(id)
# id_office_t1 <- location_t1 %>% filter(location == rooms[rooms$id == "M-PE", "id_room"]) %>% pull(id)
# id_not_here_t1 <- location_t1 %>% filter(location == -1 ) %>% pull(id)
# 
# 
# for (individual in id_not_interacting_t2){
#   if (individual %in% id_paramedical){
#     ind_loc_t2 <- case_when(
#       individual %in% id_room_t1 ~ rooms[rooms$id == "ALL", "id_room"],
#       individual %in% id_nursing_station_t1 ~ rooms[rooms$id == "ALL", "id_room"],
#       individual %in% id_paramedical_restroom_t1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
#       individual %in% id_corridor_t1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
#       individual %in% id_not_here_t1 ~ -1,
#       .default = -2 #"ERROR - WRONG LOC MED t2"
#     )
#   } else if (individual %in% id_medical){
#     ind_loc_t2 <- case_when(
#       individual %in% id_room_t1 ~ rooms[rooms$id == "ALL", "id_room"],
#       individual %in% id_nursing_station_t1 ~ rooms[rooms$id == "ALL", "id_room"],
#       individual %in% id_office_t1 ~ rooms[rooms$id == "ALL", "id_room"],
#       individual %in% id_medical_restroom_t1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
#       individual %in% id_corridor_t1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
#       individual %in% id_not_here_t1 ~ -1,
#       .default = -3 #"ERROR - WRONG LOC MED t2"
#     )
#   } else {
#     ind_loc_t2 <- -4 #"ERROR - ID NOT IN MED/PARAMED"
#   }
#   ## ASSIGN THE location OF THE INDIVIDUAL AT t==2
#   location_t2[location_t2$id == individual, "location"] <- ind_loc_t2
# }
# 
# ## CHANGE THE GLOBAL location DATAFRAME AT t==2
# global_location[[2]]$location <- location_t2$location
#     
# rm(location_t1,
#    location_t2,
#    id_not_interacting_t2,
#    id_room_t1,
#    id_corridor_t1,
#    id_not_here_t1,
#    id_medical_restroom_t1,
#    id_paramedical_restroom_t1,
#    id_nursing_station_t1,
#    id_office_t1,
#    ind_loc_t2)

```

```{r Loc tsup2}
# ############
# ## t > 2 ###
# ############
# for (t in 3:n_subdivisions){
#   location_t <- global_location[[t]]
#   location_tm1 <- global_location[[t-1]]
#   
#   id_not_interacting_t <- location_t %>% filter(is.na(location)) %>% pull(id)
#   
#   id_room_tm1 <- location_tm1 %>% filter(location %in% id_room_patient) %>% pull(id)
#   id_corridor_tm1 <- location_tm1 %>% filter(location == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
#   id_office_tm1 <- location_tm1 %>% filter(location == rooms[rooms$id == "M-PE", "id_room"]) %>% pull(id)
#   id_medical_restroom_tm1 <- location_tm1 %>% filter(location == rooms[rooms$id == "R-M-PE", "id_room"]) %>% pull(id)
#   id_nursing_station_tm1 <- location_tm1 %>% filter(location == rooms[rooms$id == "PM-PE", "id_room"]) %>% pull(id)
#   id_paramedical_restroom_tm1 <- location_tm1 %>% filter(location == rooms[rooms$id == "R-PM-PE", "id_room"]) %>% pull(id)
#   
#   id_not_here_tm1 <- location_tm1 %>% filter(location == -1 ) %>% pull(id)
#   
#   ## ITERATE ON THE INDIVIDUALS NOT INTERACTING at time t
#   for (individual in id_not_interacting_t){
#     shifts_j <- shifts[shifts$individual == individual, ]
#     current_time <- begin_date + t * 30
#     in_shift <- any(current_time >= shifts_j$start_time & current_time <= shifts_j$end_time)
#     
#     if (in_shift) {
#       ## If the individual is within a shift
#       
#       if (individual %in% id_paramedical){
#         ind_loc_t <- case_when(
#           individual %in% id_room_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
#           individual %in% id_nursing_station_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
#           individual %in% id_paramedical_restroom_tm1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
#           individual %in% id_corridor_tm1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
#           individual %in% id_not_here_tm1 ~ -1,
#           .default = -5 #"ERROR - WRONG LOC PARAMED t>2"
#         )
#       } else if (individual %in% id_medical){
#         ind_loc_t <- case_when(
#           individual %in% id_room_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
#           individual %in% id_nursing_station_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
#           individual %in% id_office_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
#           individual %in% id_medical_restroom_tm1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
#           individual %in% id_corridor_tm1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
#           individual %in% id_not_here_tm1 ~ -1,
#           .default = -6 #"ERROR - WRONG LOC MED t>2"
#         )
#       } else {
#         ind_loc_t <- -7 #"ERROR - ID NOT IN MED/PARAMED t>2"
#         }
#     } else {
#       ## If the individual is not within a shift
#       ind_loc_t <- -1 #"NOT HERE"
#     }
#     ## ASSIGN THE location OF THE INDIVIDUAL AT t>2
#     location_t[location_t$id == individual, "location"] <- ind_loc_t
#   }
#   
#   global_location[[t]] <- location_t
# }
```
